The Kapowski Chronicles: A Complete, Volumetric Cortical Thickness Open Source Pipeline with Evaluation on Public Data

### 2013-05-28 KapowskiChronicles/methods.tex
ENH:  James C. Edwards

\begin{figure}
  \centering
  \includegraphics[width=90mm]{Figures/template50_60.pdf}
  \caption{Sample multivariate template constructed from a subset of the IXI data (female, age 50--60).  Axial slices of five of the 37 total subjects from this cohort are shown. }
  \label{fig:template}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=90mm]{Figures/templates.pdf}
  \caption{Population-specific templates for each of the four public data sets used 
  for cortical thickness 
  estimation generated using the script antsMultivariateTemplateConstruction.sh. 
  The benefit of using such templates is obvious considering the variability in
  acquisition and data preparation (e.g. defacing protocols).
  }
  \label{fig:template}
\end{figure}
